### 2017-06-27 README.Rmd
Add "Implemented" tags in README
split hypotheses into null and parameters

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesize(null = "p = 25") %>% # would require string parsing
  generate(reps = 100, type = "permute") %>% # here it’d be doing simulation
  calculate(stat = "prop") #
```

@@

One categorical (>2 level) - GoF
```
mtcars %>%
  select(cyl) %>%
  hypothesize(null = "p1 = .33, p2 = .33, p3 = .33") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

@@

```
mtcars %>%
  select(mpg, am) %>%
  hypothesize(null = "equal means") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in means")
```

One numerical one categorical (>2 levels) -  ANOVA
```
mtcars %>%
  select(mpg, cyl) %>%
  hypothesize(null = "equal means") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "F")
```

@@

One numerical (one mean)
```
mtcars %>%
  select(mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "mean")
```

>>>>

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesize(null = "point", p = .25) %>% 
  generate(reps = 100, type = "simulation") %>% 
  calculate(stat = "prop") #
```

@@

One categorical (>2 level) - GoF
```
mtcars %>%
  select(cyl) %>%
  hypothesize(null = "point", p1 = .25, p2 = .25, p3 = .50) %>% # call levels() to find order of p's
  generate(reps = 100, type = "simulate") %>%
  calculate(stat = "chisq")
```

@@

```
mtcars %>%
  select(mpg, am) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in means")
```

One numerical one categorical (>2 levels) -  ANOVA
```
mtcars %>%
  select(mpg, cyl) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "F")
```

@@

One numerical (one mean)

```
mtcars %>%
  select(mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "mean")
```
